Data Exploration

### 2019-02-26 src/stack_test.Rmd
stack predict loop done

  }
   # st19980186.9 <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
  }
#st19980186.9
```

>>>>

  }
   st19980186.9 <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
  }
st19980186.9
```

messing with code to see if can do for unique year month depth

need tidyr package
```{r}
unyears <- as.character(c("1998", "1999", "2000", "2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014", "2015")) 
#unyears <- paste0("X", unyears) #this adds an X to each year to match with raster naming
unmonths <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12")
undepths <- c("0.505760014", "1.55585527", "2.66768169", "3.85627985" , "5.14036131", "6.5430336", "8.09251881", "9.82275009", "11.7736797" , "13.9910383", "16.525322" , "19.4298019", "22.757616", "26.5583", "30.8745613", "35.7402039", "41.1800232", "47.211895", "53.8506355", "61.1128387" , "69.0216827" , "77.6111603", "86.9294281", "97.0413132", "108.030281", "120", "133.075821", "147.40625", "163.164459" , "180.549927", "199.789963", "221.141174", "244.890625" , "271.356384", "300.887512", "333.862823" , "370.688477", "411.793854", "457.62561", "508.639893", "565.292297", "628.026001", "697.258667", "773.368286", "856.678955", "947.447876", "1045.85425", "1151.99121", "1265.86145", "1387.37695", "1045.854", "1151.99097", "1265.86096") #this is biomer + the 3 glorys layers that are different... but that's not the best way because you are creating extra depth rows here... actually recommend you rename the asc files in windows powershell to match

unlayer <- crossing(unyears, unmonths, undepths)
unlayer$stackname <- paste0("st", unlayer$unyears, unlayer$unmonths, unlayer$undepths) #this creates the name of the stack that will be used
unlayer$temp_depth <- NA
unlayer$temp_surface <- NA
unlayer$chl_depth <- NA
unlayer$chl_surface <- NA
unlayer$o2_depth <- NA
unlayer$o2_surface <- NA
unlayer$salinity_depth <- NA
unlayer$salinity_surface <- NA
unlayer$nao_sample <- NA
unlayer$nao_prev <- NA
unlayer$nao_winter <- NA
unlayer$amo_sample <- NA
unlayer$amo_prev <- NA
unlayer$amo_winter <- NA

ascname <- list.files("../data/jan_test_86.9/", pattern = "*.asc", full.names = FALSE)    # this folder currently contains other dummy files. its just a test to automate stacks
ascpath <- list.files("../data/jan_test_86.9/", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks

for (k in 1:nrow(unlayer)){
    print(unlayer$stackname[k])
    year <- unlayer$unyears[k]
    month <- unlayer$unmonths[k]
    depth <- unlayer$undepths[k]
    for (i in 1:length(ascname)){

    ascyear <- (sapply(strsplit(ascname[[i]], "_"), "[[", 1))
    ascmonth <- (sapply(strsplit(ascname[[i]], "_"), "[[", 2))
    ascdepth <- (sapply(strsplit(ascname[[i]], "_"), "[[", 5))
    ascdepth <- gsub(".asc", "", ascdepth)
    ascvar1 <- (sapply(strsplit(ascname[[i]], "_"), "[[", 3))
    ascvar2 <- (sapply(strsplit(ascname[[i]], "_"), "[[", 4))
    ascfile <- ascpath[[i]]
    print(ascfile)

    if (ascyear == year & ascmonth == month & ascvar1 == tempvar & ascvar2 == depthvar & ascdepth == depth){
    unlayer$temp_depth[k] <- ascfile
  } else if (ascyear == year & ascmonth == month & ascvar1 == chlvar & ascvar2 == surfacevar & ascdepth == depth){
   unlayer$chl_surface[k] <- ascfile
 } else if (ascyear == year & ascmonth == month & ascvar1 == o2var & ascvar2 == depthvar & ascdepth == depth){
  unlayer$o2_depth[k] <- ascfile
 } else if (ascyear == year & ascmonth == month & ascvar1 == salvar & ascvar2 == depthvar & ascdepth == depth){
  unlayer$salinity_depth[k] <- ascfile
 } else if (ascyear == year & ascmonth == month & ascvar1 == naovar & ascvar2 == wintervar){
  unlayer$nao_winter[k] <- ascfile
 } else if (ascyear == year & ascmonth == month  & ascvar1 == naovar & ascvar2 == samplevar){
  unlayer$nao_sample[k] <- ascfile
 }

    }
    write.csv(unlayer, "../data/env/asc_layerlist.csv", row.names = TRUE)
}

# now loop to create stacks
unlayer <- read.csv("../data/env/asc_layerlist.csv", header = TRUE)
unlayer[] <- lapply(unlayer, as.character) #from https://stackoverflow.com/questions/2851015/convert-data-frame-columns-from-factors-to-characters

for (td in 1:nrow(unlayer)){
  temp_depth <- raster(unlayer$temp_depth[td])
  names(temp_depth) <- "temp_depth"
  chl_surface <- raster(unlayer$chl_surface[td])
  names(chl_surface) <- "chl_surface"
  o2_depth <- raster(unlayer$o2_depth[td])
  names(o2_depth) <- "o2_depth"
  salinity_depth <- raster(unlayer$salinity_depth[td])
  names(salinity_depth) <- "salinity_depth"
  nao_sample <- raster(unlayer$nao_sample[td])
  names(nao_sample) <- "nao_sample"
  nao_winter <- raster(unlayer$nao_winter[td])
  names(nao_winter) <- "nao_winter"
  stackn <- unlayer$stackname[td]
  test <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
  #stackSave(test,unlayer$stackname[td])
  pred <- predict(mod1, test, file = paste0("../output/maxentpredict/", stackn), overwrite=TRUE) 
  preplot <- plot(pred, png(paste0("../output/maxentpredict/", stackn, ".png")))
  paste("maxplot_", stackn, ".png", sep = "") # to automatically save the plot to a png AND show it inline

}
dev.off() # stops automatic saving of the plot to a png
# now call the stack...
{
stack <- stackOpen("st19920310.stk")
}
```

  preplot <- plot(pred, png(paste0(stackn, ".png")))

```{r}
var <- raster(stacktest$chl[1])
var
a <- raster(var)
a
```

#maxent
maxnet throwing errors...
```{r}
janpres <- read.csv("../output/bio/maxenttestjanpr.csv", header = TRUE)
janpres$occ <- 1
janab <- read.csv("../output/bio/maxenttestjanab.csv", header = TRUE)
janab$occ <- 0
prab <- rbind(janpres, janab)
prab$originalscientificname <- "cap" #because species name needs to be the same
pa <- prab$occ
prab <- subset(prab, select = -c(x, y, occ, originalscientificname)) #ok so for maxent in r just need the variables
prab

system.file("java", package="dismo") #finding location to put maxent jar file
system("java -version")
mod1 <- maxent(x = prab, p = pa, path = paste0("../output/maxentout"), args =  c("responsecurves"), save(md, file = "../output/maxentmod"))
pre1 <- predict(mod1, test) #,  args='outputformat=cloglog'
plot(pre1)
plot(mod1)

plot(pre1)
```
